This page and the next page should be removed

### 2021-01-18 analysis/manuscript.Rmd
write function to compute single trial amplitudes in python

```{r setup, include=FALSE}
# Do you want to re-run the EEG preprocessing? Note that this can only be done with the raw data,
# which are available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
rerun_preproc <- FALSE

# Do you want to re-run the linear mixed-effect models? This can be done even if only the
# preprocessed single-trial data are available (from GitHub and/or the OSF). Note, however, that
# fitting all models may take 24 hours or more.
rerun_models <- FALSE

@@

# Define ERP components of interest
comps <- tibble(
  name = c("P1", "N170", "N400"),
  start = c(100, 150, 400),
  stop = c(150, 200, 700),
  roi = list(
    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
  )
)
```

@@

# Define function for preprocessing the EEG data
def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq,
            event_id, tmin, tmax, baseline, reject):
    # Read EEG data in microvolts
    raw = mne.io.read_raw_brainvision(vhdr_fname, scale=1e6, preload=True)
    # Create virtual EOG channels
    raw = mne.set_bipolar_reference(raw, 'Auge_u', 'Fp1', ch_name='VEOG', drop_refs=False)
    raw = mne.set_bipolar_reference(raw, 'F9', 'F10', ch_name='HEOG', drop_refs=False)
    raw.set_channel_types(mapping={'VEOG': 'eog', 'HEOG': 'eog'})
    # Add EasyCap electrode layout, removing any excessive channels
    montage = mne.channels.make_standard_montage('easycap-M1')
    raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(['VEOG', 'HEOG'])))
    raw.set_montage(montage=montage)
    # Re-reference to common average
    raw, _ = mne.set_eeg_reference(raw, 'average')
    # Run ICA on a copy of the data
    filt_raw = raw.copy()
    filt_raw.load_data().filter(l_freq=1, h_freq=None)
    ica = mne.preprocessing.ICA(n_components=n_components, random_state=12345, method=method)
    ica.fit(filt_raw)
    # Remove bad components based on correlations with EOG
    eog_indices, eog_scores = ica.find_bads_eog(raw)
    ica.exclude = eog_indices
    raw = ica.apply(raw)
    # Apply band-pass filter
    raw = raw.filter(l_freq=l_freq, h_freq=h_freq)
    # Epoching including baseline correction
    events, _ = mne.events_from_annotations(raw, verbose=False)
    epochs = mne.Epochs(raw, events=events, event_id=event_id, tmin=tmin,
                        tmax=tmax, baseline=baseline, preload=True)
    # Add behavioral data
    epochs.metadata = metadata
    # Reject bad epochs
    epochs = epochs.drop_bad(reject=reject)
    return epochs

# Define function to compute averaged waveforms by part and condition
def compute_evokeds(epochs, grand=True, data_only=True):
  # Define lists of participants, parts, and conditions
  ps = epochs.metadata['participant'].unique()
  pts = ['I', 'II', 'III']
  cns = ['Informed', 'Naive']
  # Define function to compute a single by-participant waveform
  def compute_evoked(epochs, pt, cn, p):
    query = 'participant == "' + p + '" and part == "' + pt + '" and condition == "' + cn + '"'
    return(epochs[query].average())
  # Create a dict with by-participant waveforms nested in conditions nested in parts
  avgs = {pt:{cn:[compute_evoked(epochs, pt, cn, p) for p in ps] for cn in cns} for pt in pts}
  # If needed, compute grand-averaged waveforms across participants
  if grand:
    avgs = {pt:{cn:mne.grand_average(avgs[pt][cn]) for cn in cns} for pt in pts}
  # If needed, extract only the data from the evoked MNE objects
  if data_only:
    if grand:
      avgs = {pt:{cn:avgs[pt][cn].data for cn in cns} for pt in pts}
    else:
      avgs = {pt:{cn:[avgs[pt][cn][p].data for p in range(0, len(ps))] for cn in cns} for pt in pts}
  return(avgs)

@@

# Actually apply the preprocessing function for Epxeriment 1 in Python
map2(
  .x = list.files("data/exp1/EEG", pattern = ".vhdr", full.names = TRUE),
  .y = behav_exp1,
  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
) %>%
  # Concatenate epochs of all participants
  py$mne$epochs$concatenate_epochs() -> epochs_exp1

@@

@@

# Create a vector with sample time points (in ms)
sfreq <- epochs_exp1$info["sfreq"]
seq(preproc_params$tmin * 1000, preproc_params$tmax * 1000, 1 / sfreq * 1000) %T>%
  cat(file = "analysis/export/sample_times.tsv", sep = "\n") -> times

# Define function to compute single-trial mean ERP amplitudes
compute_erps <- function(epochs, name, start, stop, roi) {
  dat <- epochs$get_data()
  els <- epochs$ch_names
  erps <- dat[, which(els %in% roi), which(times %in% start:stop)]
  amps <- apply(erps, 1, mean, na.rm = TRUE)
  return(amps)
}

# Actually apply the function to compute mean ERP amplitudes for Experiment 1
pmap_dfc(comps, compute_erps, epochs = epochs_exp1) %>%
  set_names(comps$name) %>%
  # Bind to the behavioral data
  bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
  # Backup to the export folder
  write_tsv("analysis/export/exp1-erps.tsv") -> data_exp1

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp1-gavgs.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp1, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
  write_tsv("analysis/export/exp1-objects.tsv")
```

```{r exp1-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("analysis/export/exp1-erps.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp1

@@

# Define function to compute LMMs and follow-up contrasts for each component
compute_models <- function(dep, formula, data, control, specs) {
  require(lmerTest)
  require(buildmer)
  require(emmeans)
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  build <- buildmer(
    control = control,
    REML = FALSE,
    buildmerControl = buildmerControl(
      formula = formula,
      data = data,
      direction = c("order", "backward"),
      elim = function(logp) exp(logp) >= .20,
      calc.anova = TRUE,
      ddf = "Satterthwaite",
      dep = dep
    )
  )
  means <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$emmeans
  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts
  modlist <- list(
    model = build@model,
    anova = build@anova,
    summary = build@summary,
    means = means %>% as.data.frame(),
    contrasts = conts %>% as.data.frame()
  )
  return(modlist)
}

# Actually apply the function to compute the models for Experiment 1
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = data_exp1,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/exp1-mods.RDS") -> models_exp1
```

@@

# Load preprocessed single-trial data
read_tsv("analysis/export/exp1-erps.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp1

@@

# Load grand-averaged ERPs and linear mixed models
evokeds_exp1 <- readRDS("analysis/export/exp1-gavgs.RDS")
models_exp1 <- readRDS("analysis/export/exp1-mods.RDS")
```

@@

# Define function to plot ERP waveforms and topographies
plot_erps <- function(comps, evokeds, models, montage) {
  suppressWarnings(suppressMessages(
    pmap(comps, function(name, start, stop, roi) {
      # N400 gets a different scale than P1 and N170
      ymin <- ifelse(name == "N400", -3, -4)
      # Loop through parts
      parts <- map(c("I", "II", "III"), function(part) {
        # Create (conditions x time points) x electrodes tibble
        data_plot <- evokeds[[part]] %>%
          map(function(data) {
            data %>%
              t() %>%
              as_tibble(.name_repair = "unique") %>%
              set_colnames(montage$electrode) %>%
              mutate(.time = times, roi = rowMeans(select(., all_of(roi))))
          }) %>% bind_rows(.id = "condition")
        # Shade background depending on whether the effect is significant or not
        asterisks <- models[[name]]$contrasts %>%
          filter(part == !!part) %>%
          mutate(asterisks = case_when(p.value < .001 ~ "***", p.value < .01 ~ "**", p.value < .05 ~ "*")) %>%
          pull(asterisks)
        xasterisks <- case_when(str_length(asterisks) == 1 ~ start + 11, str_length(asterisks) == 3 ~ start + 15)
        if (is.na(asterisks)) {
          shade <- annotate("rect", xmin = start, xmax = stop, ymin = ymin + 0.1, ymax = ymin + 11.95, color = "black", fill = NA)
        } else {
          shade <- annotate("rect", xmin = start, xmax = stop, ymin = ymin + 0.1, ymax = ymin + 11.95, color = "black", fill = "gray90")
        }

        # # Prepare waveform
        # wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
        #   annotate("rect", xmin = start, xmax = stop, ymin = -Inf, ymax = ymin + 12, fill = "gray90")
        # # Shade significant area
        # star <- stars[[name]][[part]]
        # if (!is.na(star)) {
        #   wave <- wave + geom_ribbon(
        #     data = data_plot %>% filter(.time >= start & .time <= stop) %>%
        #       group_by(.time) %>% summarize(ymin = min(roi), ymax = max(roi)),
        #     aes(x = .time, xmin = start, xmax = stop, ymin = ymin, ymax = ymax),
        #     inherit.aes = FALSE, fill = viridisLite::viridis(n = 1, begin = 1)
        #   )
        # } +
        # annotate("text", label = star, x = start + (stop - start)/2, y = -3.2, size = 7, family = "Helvetica")}
        # Add waves and styling

        # Plot waveform
        wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
          shade +
          annotate("text", label = asterisks, x = xasterisks, y = ymin + 11, size = 6, hjust = 0, family = "Helvetica") +
          annotate("segment", x = -200, xend = 800, y = 0, yend = 0) +
          annotate("segment", x = 0, xend = 0, y = ymin, yend = ymin + 12) +
          annotate("segment", x = seq(-100, 700, 200), xend = seq(-100, 700, 200), y = -0.3, yend = 0) +
          annotate("segment", x = -12, xend = 0, y = seq(-2, 8, 4), yend = seq(-2, 8, 4)) +
          annotate("text", x = seq(-100, 700, 200), y = -0.9, label = seq(-100, 700, 200), size = 10 / .pt, family = "Helvetica") +
          annotate("text", x = -20, y = seq(-2, 8, 4), label = seq(-2, 8, 4), size = 10 / .pt, family = "Helvetica", hjust = 1) +
          annotate("text", x = 400, y = ymin + 0.8, label = "Time (ms)", size = 10 / .pt, family = "Helvetica", lineheight = 0.9) +
          annotate("text", x = -100, y = 4, label = paste(name, "ampl.\n(µV)"), size = 10 / .pt, family = "Helvetica", angle = 90, lineheight = 0.9) +
          geom_line() +
          scale_color_viridis_d(begin = 0.1, end = 0.5) +
          coord_cartesian(xlim = c(-200, 800), ylim = c(ymin, ymin + 14), expand = FALSE) +
          theme_void() +
          theme(legend.position = "none")
        # Plot topography
        topo <- data_plot %>%
          filter(.time >= start & .time <= stop) %>%
          group_by(condition) %>%
          summarise(across(montage$electrode, mean)) %>%
          pivot_longer(-condition) %>%
          pivot_wider(names_from = condition) %>%
          transmute(amplitude = Informed - Naive) %>%
          bind_cols(montage) %>%
          eegUtils::topoplot(limits = c(-1, 1), palette = "viridis", contour = FALSE, highlights = roi, scaling = 0.1) +
          theme(legend.position = "none")
        topo$layers[[3]]$aes_params$size <- topo$layers[[4]]$aes_params$size <- topo$layers[[5]]$aes_params$size <- 0.6
        # Combine waveform and topography
        wave + draw_plot(topo, width = 320, height = 9, x = 500, y = ymin + 6.4)
      })
      # Combine plots for the different parts
      plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))
      # Combine plots for the different components
    }) %>% plot_grid(plotlist = ., nrow = 3)
  ))
}

@@

# Apply the preprocessing function for Epxeriment 2 in Python
map2(
  .x = list.files("data/exp2/EEG", pattern = ".vhdr", full.names = TRUE),
  .y = behav_exp2,
  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
) %>%
  # Concatenate epochs of all participants
  py$mne$epochs$concatenate_epochs() -> epochs_exp2

@@

# Apply the function to compute mean ERP amplitudes for Experiment 2
pmap_dfc(comps, compute_erps, epochs = epochs_exp2) %>%
  set_names(comps$name) %>%
  # Bind to the behavioral data
  bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
  # Backup to the export folder
  write_tsv("analysis/export/exp2-erps.tsv") -> data_exp2

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp2-gavgs.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp2, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
  write_tsv("analysis/export/exp2-objects.tsv")
```

```{r exp2-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("analysis/export/exp2-erps.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp2

# Apply these contrasts to the factors in the data
contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_exp2$part) <- MASS::ginv(contrasts_part)

# Apply the function to compute the models for Experiment 2
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = data_exp2,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/exp2-mods.RDS") -> models_exp2
```

@@

# Load preprocessed single-trial data
read_tsv("analysis/export/exp2-erps.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp2

@@

# Load grand-averaged ERPs and linear mixed models
evokeds_exp2 <- readRDS("analysis/export/exp2-gavgs.RDS")
models_exp2 <- readRDS("analysis/export/exp2-mods.RDS")
```

@@

# Apply the function to compute the joint models for Experiments 1 and 2
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_subs,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/joint-mods.RDS") -> models_joint
```

```{r joint-table, include=TRUE, results="asis"}
# Load linear mixed models
models_joint <- readRDS("analysis/export/joint-mods.RDS")

@@

# Apply the function to re-compute the joint models
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_subs,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/joint-control-mods.RDS") -> models_joint_control
```

@@

# Load linear mixed models
models_joint_control <- readRDS("analysis/export/joint-control-mods.RDS")

>>>>

```{r setup, include=FALSE}
# Do you want to re-run the EEG preprocessing? Note that this can only be done with the raw data,
# which are available from the corresponding author (rasha.abdel.rahman@hu-berlin.de) upon request.
rerun_preproc <- TRUE

# Do you want to re-run the linear mixed-effect models? This can be done even if only the
# preprocessed single-trial data are available (from GitHub and/or the OSF). Note, however, that
# fitting all models may take 24 hours or more.
rerun_models <- TRUE

@@

# Define ERP components of interest
comps <- tibble(
  name = c("P1", "N170", "N400"),
  tmin = c(100, 150, 400),
  tmax = c(150, 200, 700),
  roi = list(
    c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
    c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
    c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
  )
)
```

@@

# Define function for preprocessing the EEG data
def preproc(vhdr_fname, metadata, n_components, method, l_freq, h_freq, event_id, tmin, tmax,
    baseline, reject):
    # Read EEG data in microvolts
    raw = mne.io.read_raw_brainvision(vhdr_fname, scale=1e6, preload=True)
    # Create virtual EOG channels
    raw = mne.set_bipolar_reference(raw, "Auge_u", "Fp1", ch_name="VEOG", drop_refs=False)
    raw = mne.set_bipolar_reference(raw, "F9", "F10", ch_name="HEOG", drop_refs=False)
    raw.set_channel_types(mapping={"VEOG": "eog", "HEOG": "eog"})
    # Add EasyCap electrode layout, removing any excessive channels
    montage = mne.channels.make_standard_montage("easycap-M1")
    raw.drop_channels(list(set(raw.ch_names) - set(montage.ch_names) - set(["VEOG", "HEOG"])))
    raw.set_montage(montage=montage)
    # Re-reference to common average
    raw, _ = mne.set_eeg_reference(raw, "average")
    # Run ICA on a copy of the data
    filt_raw = raw.copy()
    filt_raw.load_data().filter(l_freq=1, h_freq=None)
    ica = mne.preprocessing.ICA(n_components=n_components, random_state=12345, method=method)
    ica.fit(filt_raw)
    # Remove bad components based on correlations with EOG
    eog_indices, eog_scores = ica.find_bads_eog(raw)
    ica.exclude = eog_indices
    raw = ica.apply(raw)
    # Apply band-pass filter
    raw = raw.filter(l_freq=l_freq, h_freq=h_freq)
    # Epoching including baseline correction
    events, _ = mne.events_from_annotations(raw, verbose=False)
    epochs = mne.Epochs(
        raw, events=events, event_id=event_id, tmin=tmin, tmax=tmax, baseline=baseline, preload=True
    )
    # Add behavioral data
    epochs.metadata = metadata
    # Reject bad epochs
    epochs = epochs.drop_bad(reject=reject)
    return epochs

# Define function to compute averaged waveforms by part and condition
def compute_evokeds(epochs, grand=True, data_only=True):
    # Define lists of participants, parts, and conditions
    ps = epochs.metadata["participant"].unique()
    pts = ["I", "II", "III"]
    cns = ["Informed", "Naive"]
    # Define function to compute a single by-participant waveform
    def compute_evoked(epochs, pt, cn, p):
        query = 'participant == "' + p + '" and part == "' + pt + '" and condition == "' + cn + '"'
        return epochs[query].average()
    # Create a dict with by-participant waveforms nested in conditions nested in parts
    avgs = {pt: {cn: [compute_evoked(epochs, pt, cn, p) for p in ps] for cn in cns} for pt in pts}
    # If needed, compute grand-averaged waveforms across participants
    if grand:
        avgs = {pt: {cn: mne.grand_average(avgs[pt][cn]) for cn in cns} for pt in pts}
    # If needed, extract only the data from the evoked MNE objects
    if data_only:
        if grand:
            avgs = {pt: {cn: avgs[pt][cn].data for cn in cns} for pt in pts}
        else:
            ps_num = range(0, len(ps))
            avgs = {pt: {cn: [avgs[pt][cn][p].data for p in ps_num] for cn in cns} for pt in pts}
    return avgs

# Define function to compute single-trial mean ERP ampltiudes from epochs
def compute_erps(epochs, name, tmin, tmax, roi):
    # Average across electrodes in the ROI
    roi_idx = mne.pick_channels(epochs.ch_names, roi)
    epochs_roi = mne.channels.combine_channels(epochs, dict(roi=roi_idx))
    # Average across samples in the time window
    import numpy as np
    tmin_s, tmax_s = tmin / 1000, tmax / 1000
    times_idx = np.where(np.logical_and(epochs.times >= tmin_s, epochs.times <= tmax_s))
    erps = epochs_roi.get_data()[:, 0, times_idx].mean(axis=(1, 2))
    return erps

@@

# Preprocess the EEG for Epxeriment 1 in Python
map2(
  .x = list.files("data/exp1/EEG", pattern = ".vhdr", full.names = TRUE),
  .y = behav_exp1,
  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
) %>%
  # Concatenate epochs of all participants
  py$mne$epochs$concatenate_epochs() -> epochs_exp1

@@

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp1) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
  write_tsv("analysis/export/exp1-data.tsv") -> data_exp1

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp1-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp1, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
  write_tsv("analysis/export/exp1-objects.tsv")

@@

# Remove the epochs to free up memory
rm(epochs_exp1)
```

```{r exp1-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known"
    )),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp1

@@

# Define function to compute LMMs and follow-up contrasts for each component
compute_models <- function(dep, formula, data, control, specs) {
  require(lmerTest)
  require(buildmer)
  require(emmeans)
  emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
  build <- buildmer(
    control = control,
    REML = FALSE,
    buildmerControl = buildmerControl(
      formula = formula,
      data = data,
      direction = c("backward", "backward"),
      elim = function(logp) exp(logp) >= .20,
      calc.anova = TRUE,
      ddf = "Satterthwaite",
      dep = dep
    )
  )
  means <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$emmeans
  conts <- emmeans(build@model, specs = specs, infer = TRUE, data = data)$contrasts
  modlist <- list(
    model = build@model,
    anova = build@anova,
    summary = build@summary,
    means = means %>% as.data.frame(),
    contrasts = conts %>% as.data.frame()
  )
  return(modlist)
}

# Compute the models for Experiment 1
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = data_exp1,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/exp1-models.RDS") -> models_exp1
```

@@

# Load preprocessed single-trial data
read_tsv("analysis/export/exp1-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp1

@@

# Load grand-averaged ERPs and linear mixed models
evokeds_exp1 <- readRDS("analysis/export/exp1-gaverages.RDS")
models_exp1 <- readRDS("analysis/export/exp1-models.RDS")
```

@@

# Define function to plot ERP waveforms and topographies
plot_erps <- function(comps, evokeds, models, montage) {
  suppressWarnings(suppressMessages(
    pmap(comps, function(name, tmin, tmax, roi) {
      # N400 gets a different scale than P1 and N170
      ymin <- ifelse(name == "N400", -3, -4)
      # Loop through parts
      parts <- map(c("I", "II", "III"), function(part) {
        # Create (conditions x time points) x electrodes tibble
        data_plot <- evokeds[[part]] %>%
          map(function(data) {
            data %>%
              t() %>%
              as_tibble(.name_repair = "unique") %>%
              set_colnames(montage$electrode) %>%
              mutate(.time = seq(-500, 1498, 2), roi = rowMeans(select(., all_of(roi))))
          }) %>% bind_rows(.id = "condition")
        # Shade background depending on whether the effect is significant or not
        asterisks <- models[[name]]$contrasts %>%
          filter(part == !!part) %>%
          mutate(asterisks = case_when(p.value < .001 ~ "***", p.value < .01 ~ "**", p.value < .05 ~ "*")) %>%
          pull(asterisks)
        xasterisks <- case_when(str_length(asterisks) == 1 ~ tmin + 11, str_length(asterisks) == 3 ~ tmin + 15)
        if (is.na(asterisks)) {
          shade <- annotate("rect", xmin = tmin, xmax = tmax, ymin = ymin + 0.1, ymax = ymin + 11.95, color = "black", fill = NA)
        } else {
          shade <- annotate("rect", xmin = tmin, xmax = tmax, ymin = ymin + 0.1, ymax = ymin + 11.95, color = "black", fill = "gray90")
        }

        # # Prepare waveform
        # wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
        #   annotate("rect", xmin = tmin, xmax = tmax, ymin = -Inf, ymax = ymin + 12, fill = "gray90")
        # # Shade significant area
        # star <- stars[[name]][[part]]
        # if (!is.na(star)) {
        #   wave <- wave + geom_ribbon(
        #     data = data_plot %>% filter(.time >= tmin & .time <= tmax) %>%
        #       group_by(.time) %>% summarize(ymin = min(roi), ymax = max(roi)),
        #     aes(x = .time, xmin = tmin, xmax = tmax, ymin = ymin, ymax = ymax),
        #     inherit.aes = FALSE, fill = viridisLite::viridis(n = 1, begin = 1)
        #   )
        # } +
        # annotate("text", label = star, x = tmin + (tmax - tmin)/2, y = -3.2, size = 7, family = "Helvetica")}
        # Add waves and styling

        # Plot waveform
        wave <- ggplot(data = data_plot, aes(x = .time, y = roi, color = condition)) +
          shade +
          annotate("text", label = asterisks, x = xasterisks, y = ymin + 11, size = 6, hjust = 0, family = "Helvetica") +
          annotate("segment", x = -200, xend = 800, y = 0, yend = 0) +
          annotate("segment", x = 0, xend = 0, y = ymin, yend = ymin + 12) +
          annotate("segment", x = seq(-100, 700, 200), xend = seq(-100, 700, 200), y = -0.3, yend = 0) +
          annotate("segment", x = -12, xend = 0, y = seq(-2, 8, 4), yend = seq(-2, 8, 4)) +
          annotate("text", x = seq(-100, 700, 200), y = -0.9, label = seq(-100, 700, 200), size = 10 / .pt, family = "Helvetica") +
          annotate("text", x = -20, y = seq(-2, 8, 4), label = seq(-2, 8, 4), size = 10 / .pt, family = "Helvetica", hjust = 1) +
          annotate("text", x = 400, y = ymin + 0.8, label = "Time (ms)", size = 10 / .pt, family = "Helvetica", lineheight = 0.9) +
          annotate("text", x = -100, y = 4, label = paste(name, "ampl.\n(µV)"), size = 10 / .pt, family = "Helvetica", angle = 90, lineheight = 0.9) +
          geom_line() +
          scale_color_viridis_d(begin = 0.1, end = 0.5) +
          coord_cartesian(xlim = c(-200, 800), ylim = c(ymin, ymin + 14), expand = FALSE) +
          theme_void() +
          theme(legend.position = "none")
        # Plot topography
        topo <- data_plot %>%
          filter(.time >= tmin & .time <= tmax) %>%
          group_by(condition) %>%
          summarise(across(montage$electrode, mean)) %>%
          pivot_longer(-condition) %>%
          pivot_wider(names_from = condition) %>%
          transmute(amplitude = Informed - Naive) %>%
          bind_cols(montage) %>%
          eegUtils::topoplot(limits = c(-1, 1), palette = "viridis", contour = FALSE, highlights = roi, scaling = 0.1) +
          theme(legend.position = "none")
        topo$layers[[3]]$aes_params$size <- topo$layers[[4]]$aes_params$size <- topo$layers[[5]]$aes_params$size <- 0.6
        # Combine waveform and topography
        wave + draw_plot(topo, width = 320, height = 9, x = 500, y = ymin + 6.4)
      })
      # Combine plots for the different parts
      plot_grid(parts[[1]], NULL, parts[[2]], NULL, parts[[3]], nrow = 1, rel_widths = c(10, 1, 10, 1, 10))
      # Combine plots for the different components
    }) %>% plot_grid(plotlist = ., nrow = 3)
  ))
}

@@

# Preprocess the EEG for Epxeriment 2 in Python
map2(
  .x = list.files("data/exp2/EEG", pattern = ".vhdr", full.names = TRUE),
  .y = behav_exp2,
  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
) %>%
  # Concatenate epochs of all participants
  py$mne$epochs$concatenate_epochs() -> epochs_exp2

@@

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp2) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp2$metadata), .) %T>%
  write_tsv("analysis/export/exp2-data.tsv") -> data_exp2

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp2, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp2-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp2, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp2$participant), .before = 1) %>%
  write_tsv("analysis/export/exp2-objects.tsv")

# Remove the epochs to free up memory
rm(epochs_exp2)
```

```{r exp2-models, eval=rerun_models}
# Load preprocessed single-trial data
read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) %>%
  # Remove any trials excluded from conditions
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() -> data_exp2

# Apply contrasts to the factors in the data
contrasts(data_exp2$condition) <- MASS::ginv(contrasts_condition)
contrasts(data_exp2$part) <- MASS::ginv(contrasts_part)

# Compute the models for Experiment 2
map(
  comps$name,
  compute_models,
  formula = formula_exp12,
  data = data_exp2,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/exp2-models.RDS") -> models_exp2
```

@@

# Load preprocessed single-trial data
read_tsv("analysis/export/exp2-data.tsv", col_types = cols()) %>%
  # Factorize columns
  mutate(
    part = factor(part, levels = c("I", "II", "III")),
    condition = factor(condition, levels = c(
      "Informed", "Naive", "Excl_informed", "Excl_naive", "Excl_known")
    ),
    participant = factor(participant),
    item = factor(item)
  ) -> data_exp2

@@

# Load grand-averaged ERPs and linear mixed models
evokeds_exp2 <- readRDS("analysis/export/exp2-gaverages.RDS")
models_exp2 <- readRDS("analysis/export/exp2-models.RDS")
```

@@

# Apply the function to compute the joint models for Experiments 1 and 2
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_subs,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/joint-models.RDS") -> models_joint
```

```{r joint-table, include=TRUE, results="asis"}
# Load linear mixed models
models_joint <- readRDS("analysis/export/joint-models.RDS")

@@

# Apply the function to re-compute the joint models
map(
  comps$name,
  compute_models,
  formula = form_joint,
  data = data_joint_subs,
  control = control,
  specs = specs_exp12
) %>%
  set_names(comps$name) %T>%
  saveRDS("analysis/export/joint-control-models.RDS") -> models_joint_control
```

@@

# Load linear mixed models
models_joint_control <- readRDS("analysis/export/joint-control-models.RDS")
